\tool: A Multi-Mode Attack Model of BadUSB

### 2021-01-24 WOOT/Files/experiment.tex
Exp up to attack scenario

\textit{Sharing Power Bank}. 
Sharing power bank provides users with short-term rental of power banks. 
The provider deploys power bank stations in the city, while the users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay the rent online.

@@

\textbf{\textit{QR Code Payment}}. 
QR code payment is a payment method where payment is typically performed as the following steps:
\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. This QR code is encoded with a globally unique ID to identify the payer's account. 
\ding{183} The payee scan the payment QR code presented by the payer. By presenting this QR code, the payer authorizes proceeding with the payment.
\ding{184} An order generated by this scan is sent to the payment service provider. Then the payment service provider requests the payer to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.

@@

In the real-world, some payment service providers provide special rules for micropayments purchases. A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. For example, WeChat Pay regards payments less than CNY \textyen 1000 as micropayments. Differing from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further action, which is often encouraged by the payment service provider.

The payment QR code is associated with the payer's account. If a victim's payment code is leaked to an attacker, an attacker can use the victim's payment code to proceed with payments. Furthermore, the attacker can use several micropayments to steal money from the victim's account while leaving the victim unconscious. In summary, the payment QR code is highly sensitive on users' devices.

@@

It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary power banks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user who unconsciously connect his/her device to \tool can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.

>>>>

\textbf{Sharing Power Bank}. 
Sharing power bank provides users with short-term rental of power banks. 
The provider deploys power bank stations in the city, while the users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay the rent online.

@@

\textbf{QR Code Payment}. 
QR code payment is a method of paying bills, typically performed as the following steps:
\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. 
This QR code is encoded with a globally unique ID to identify the payer's account. 
\ding{183} The payee scan the payment QR code presented by the payer. 
By presenting this QR code, the payer authorizes proceeding with the payment.
\ding{184} An order generated by this scan is sent to the payment service provider. 
Then the payment service provider requests the payer to confirm the transaction.
\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.
\shuqing{I think this paragraph can be shorter. No need to explain so much details.}

@@

In the real-world scenario, some payment service providers provide special rules for micropayment purchases. 
A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. 
For example, WeChat Pay~\cite{Wechat-pay} regards payments less than CNY \textyen 1000 as micropayments. 
Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further actions, which is often encouraged by the payment service provider.
The payment QR code is associated with the payer's account. 
If a victim's payment code is leaked to the attackers, they can use the that payment code to proceed payments. 
Furthermore, the attackers can use several micropayments to steal money from the victim's account, leaving the victim unconscious. 
\shuqing{Introduce something about QR code refreshing (fast).}
In summary, the payment QR code is highly sensitive on users' devices.

@@

Note that \tool exposed only a type-c cable (from USB Type-C hub),
and \tool will charge his or her device through this cable, which has no difference from ordinary power banks. Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks. The next user who unconsciously connect his/her device to \tool can find his/her devices being charged as normal.
Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code. In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.
